State of the Art in Concurrent Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-31 paper/paper.Rnw
Explain why S+L, Wimmer PQs were not benched

>>>>

Unfortunately, we were not able to obtain an implementation of the \citeauthor{shavit2000skiplist}
priority queue for benchmarking. The \citeauthor{wimmer2013data} data structure was omitted in the
following benchmarks since it is tightly coupled with the task-scheduling framework \emph{Pheet},
and cannot directly be compared to other implementations in its current form.
